
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment8.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------
```{r}
library(gganimate)
library(gifski)
library(lubridate)
library(tidyverse)
```

1. Install two packages `gganimate` and `gifski` then restart Rstudio. Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19. 
```{r}
df <- read.csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')
names(df)[1]<- 'date_reported'
df$month = month(df$date_reported)
df1 <- df %>% filter(Country == 'Ireland'|Country == 'Norway') %>% group_by(month, Country) %>% summarise(mean = mean(New_cases)) %>% mutate(rank=rank(-mean))
p1 <- df1 %>%  ggplot(aes(y=factor(rank), x=mean, group=Country, fill=Country)) + geom_col() + transition_states(month)+labs(x = 'New Cases', title = 'Month: {closest_state}')
animate(p1, nframes=100, fps=20)
```


2. Make another bar race using that dataset.  
```{r}
df$Weekday = wday(df$date_reported)
df2 <- df %>% filter(Country == 'Ireland'|Country == 'Norway') %>% group_by(Weekday, Country) %>% summarise(mean = mean(New_deaths)) %>% mutate(rank=rank(-mean))
p2 <- df2 %>% ggplot(aes(y=factor(rank),x=mean,group=Country, fill=Country)) + geom_col() + transition_states(Weekday) + labs(x = 'New Deaths', title = 'Weekday: {closest_state}')
animate(p2, nframes=100, fps=20)

```

3. Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (https://covidtracking.com/data/download/all-states-history.csv) but you should make a different bar racev from ones in the slides. 
```{r}
c <- read_csv('https://covidtracking.com/data/download/all-states-history.csv')
c$weekday = wday(c$date)
drop_na(c, hospitalized)
c1 <- c %>% filter(state %in% c('TN','SC','KY','VA'), hospitalizedIncrease>0) %>% group_by(weekday, state) %>% summarize(mean = mean(hospitalized)) %>% mutate(rank=rank(-mean))
p3 <- c1 %>% ggplot(aes(y=factor(rank), x=mean, group=state, fill=state, label=state)) + geom_col() + geom_text(aes(label = state), hjust=1.5) + transition_states(weekday) + labs(y = 'Rank', x = 'Number of Patients Hospitalized with Covid', title = 'Weekday: {closest_state}', caption = 'This bar race represents the amount of hospitalized patients with Covid in the middle south region')
animate(p3, nframes=100, fps=20)
```

