
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 9: Visualization - Revealing a graph"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment9.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```
```{r}
library(gganimate)
library(gifski)
library(lubridate)
library(tidyverse)
```


-------

1. Use the dataset by of covid 19 by WHO at https://covid19.who.int/WHO-COVID-19-global-data.csv. Find the three countries with the most numbers of deaths by Covid-19. 

Hint: 

-  Use `filter` to select the most current date 

-  Pipe with `arrange(-Cumulative_deaths)` to rank the data by the number of cumulative deaths
```{r}
df <- read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')
d <- df %>% filter(Date_reported=='2021-10-20') %>% arrange(-Cumulative_deaths)
d
```


2. Make a plot revealing the number of deaths in the three countries with the most numbers of deaths
```{r}
df %>% filter(Country_code %in% c('US','BR','IN')) %>% ggplot(aes(x=Date_reported, y=Cumulative_deaths, color=Country_code)) + geom_line() + geom_point(size=3) + transition_reveal(Date_reported)
```

3. Create the new variable (column) `death_per_cases` recording the number of deaths per cases (Hint: divide cumulative deaths by cumulative cases).  What are the three countries with the highest deaths per cases? 
```{r}
df$death_per_cases = df$Cumulative_deaths/df$Cumulative_cases
```

4. Make a plot revealing the number of deaths per cases of the US, Italy and Mexico. 
```{r}
df %>% drop_na(death_per_cases) %>% filter(Country_code %in% c('US','IT','MX')) %>% ggplot(aes(x=Date_reported, y=death_per_cases, color=Country_code)) + geom_line() + geom_point(size=3) + transition_reveal(Date_reported)
```

5. Use `transition_reveal` to create three animated graph with the vaccination data at 

https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv
```{r}
x <- read_csv('https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv')
```
```{r}
x %>% drop_na(Doses_admin) %>% filter(Province_State %in% c('Massachusetts', 'Rhode Island', 'New Hampshire'), Vaccine_Type=="All") %>% ggplot(aes(x=Date, y=Doses_admin, color=Province_State)) + geom_line() + geom_point(size=3) + transition_reveal(Date)
```
```{r}
x %>% drop_na(Doses_admin) %>% filter(Vaccine_Type %in% c('Pfizer', 'Moderna', 'Janssen'), Province_State=="Texas") %>% ggplot(aes(x=Date, y=Doses_admin, color=Vaccine_Type)) + geom_line() + geom_point(size=3) + transition_reveal(Date)
```
```{r}
x %>% drop_na(Stage_One_Doses) %>% filter(Province_State %in% c('California', 'Florida'), Vaccine_Type=="All") %>% ggplot(aes(x=Date, y=Stage_One_Doses, color=Province_State)) + geom_line() + geom_point(size=3) + transition_reveal(Date)
```



