
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 14: Twitters Mining with rtweet"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment14.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


[Sample Codes](rtweet2.html)
```{r message=FALSE, warning=FALSE}
library(rtweet) 
library(tidytext)
library(ggpubr) 
library(tidyverse) 
library(knitr)
library(lubridate)
```

-------

1. Pick a keyword or hashtag. Download the data associated with the keyword/hashtag. Plot at least 10 plots to visualize the data associated with the keyword/hashtag. All plots should have titles and captions. 
```{r message=FALSE, warning=FALSE, eval=FALSE}
keyword_search = '#countrymusic'

df <- search_tweets(q = keyword_search, 
                        n = 18000,
                        include_rts = FALSE,
                        `-filter` = "replies",
                        lang = "en") %>% mutate(created_at = ymd_hms(format(created_at, tz = "US/Eastern")))


write_csv(df, 'twitter_countrymusic.csv')
```
```{r message=FALSE, warning=FALSE}
df <- read_csv('twitter_countrymusic.csv')
```
```{r}
df %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#countrymusic",'#country','#music'), str_detect(hashtag, "^#")) %>% 
  count(hashtag, sort = TRUE) %>%
  head(10)
df %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#countrymusic",'#country','#music'), str_detect(hashtag, "^#")) %>%
  count(hashtag, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(hashtag, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r warning=FALSE}
library(RColorBrewer)
pal <- brewer.pal(8,"Dark2")
library(wordcloud) 

df %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#countrymusic",'#country','#music'), str_detect(hashtag, "^#")) %>%
  count(hashtag, sort = TRUE) %>%
  mutate(hashtag = str_remove(hashtag, '#')) %>% 
  filter(hashtag != 'country') %>% 
  with(wordcloud(hashtag, n, random.order = FALSE, max.words = 50, colors = pal))
```
```{r}
df %>% 
  count(source, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(source, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
df %>% 
  filter(!is.na(country)) %>% 
  count(country, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(country, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
df %>% 
  filter(!is.na(location), !location=='') %>% 
  count(location, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(location, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
df %>% 
  select(screen_name, favourites_count) %>% 
  filter(!is.na(favourites_count)) %>% 
  group_by(screen_name) %>% 
  summarise(average_fav = mean(favourites_count)) %>% 
  arrange(-average_fav) %>% 
  head(5) %>% 
  ggplot(aes(x=average_fav, y = reorder(screen_name, average_fav)))+
  geom_col()+
  labs(y='Account')
```
```{r}
df %>% 
  unnest_tokens(output = word, input = text, token = "words") %>%
  anti_join(get_stopwords()) %>% 
  count(word, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(word, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')

```
```{r}
ts_plot(df, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of Tweets with #countymusic",
       subtitle = paste0(format(min(df$created_at), "%d %B %Y"), " to ", format(max(df$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's rtweet API") +
  theme_minimal()
```
```{r}
df %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(word, sort = TRUE) %>%
    inner_join(get_sentiments("nrc")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(y= reorder(sentiment, n), x = n))+geom_col()+
    labs(y='Relative Frequency', x ='')
```
```{r}
df %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(word, sort = TRUE) %>%
    inner_join(get_sentiments("bing")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(y= reorder(sentiment, n), x = n))+geom_col()+
    labs(y='Relative Frequency', x ='')
```

2. Choose a location then pick a trending keyword/hashtag in the location. Download the data associated with the keyword/hashtag. Plot at least 10 plots to visualize the data associated with the keyword/hashtag. All plots should have titles and captions. 
```{r}
trends_available()
get_trends('Boston')
```
```{r}
keyword_search = '#spotify'

d <- search_tweets(q = keyword_search, 
                        n = 18000,
                        include_rts = FALSE,
                        `-filter` = "replies",
                        lang = "en") %>% mutate(created_at = ymd_hms(format(created_at, tz = "US/Eastern")))


write_csv(d, 'twitter_spotify.csv')
```
```{r}
d <- read_csv('twitter_spotify.csv')
```
```{r message=FALSE}
d %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#music", "genre", "#spotify"), str_detect(hashtag, "^#")) %>% 
  count(hashtag, sort = TRUE) %>%
  head(10)
d %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#music",'#genre', "#spotify"), str_detect(hashtag, "^#")) %>%
  count(hashtag, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(hashtag, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r warning=FALSE}
library(RColorBrewer)
pal <- brewer.pal(8,"Dark2")
library(wordcloud) 

d %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#music",'#genre','#spotify'), str_detect(hashtag, "^#")) %>%
  count(hashtag, sort = TRUE) %>%
  mutate(hashtag = str_remove(hashtag, '#')) %>% 
  filter(hashtag != 'music') %>% 
  with(wordcloud(hashtag, n, random.order = FALSE, max.words = 50, colors = pal))
```
```{r}
d %>% 
  arrange(-favorite_count) %>%
  head(5) %>% 
  select(favorite_count, text, favorite_count)
```
```{r}
d %>% 
  count(screen_name, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(screen_name, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
d %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10)
d %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10) %>% 
  ggplot(aes(x = n, y = reorder(mentions, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
d %>% 
  count(source, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(source, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
d %>% 
  filter(!is.na(country)) %>% 
  count(country, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(country, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
d %>% 
  filter(!is.na(location), !location=='') %>% 
  count(location, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(location, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
d %>% 
  select(screen_name, favourites_count) %>% 
  filter(!is.na(favourites_count)) %>% 
  group_by(screen_name) %>% 
  summarise(average_fav = mean(favourites_count)) %>% 
  arrange(-average_fav) %>% 
  head(5) %>% 
  ggplot(aes(x=average_fav, y = reorder(screen_name, average_fav)))+
  geom_col()+
  labs(y='Account')
```
```{r}
d %>% 
  unnest_tokens(output = word, input = text, token = "words") %>%
  anti_join(get_stopwords()) %>% 
  count(word, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(word, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
d %>% 
  unnest_tokens(output = word, input = text, token = "words") %>%
  anti_join(get_stopwords()) %>% 
  filter(!word %in% c('https', 't.co')) %>% 
  count(word, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(word, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
words <- d %>%
  mutate(text = str_remove_all(text, "&amp;|&lt;|&gt;"),
         text = str_remove_all(text, "\\s?(f|ht)(tp)(s?)(://)([^\\.]*)[\\.|/](\\S*)"),
         text = str_remove_all(text, "[^\x01-\x7F]")) %>% 
  unnest_tokens(word, text, token = "tweets") %>%
  filter(!word %in% stop_words$word,
        !word %in% str_remove_all(stop_words$word, "'"),
        str_detect(word, "[a-z]"),
        !str_detect(word, "^#"),         
        !str_detect(word, "@\\S+"),
        !word %in% c('united','manchester')) %>%
  count(word, sort = TRUE)

al <- brewer.pal(8,"Dark2")
library(wordcloud) 
words %>% 
  with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors = pal))
```
```{r}
ts_plot(d, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of Tweets with #spotify",
       subtitle = paste0(format(min(d$created_at), "%d %B %Y"), " to ", format(max(d$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") +
  theme_minimal()
```
```{r}
d %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(word, sort = TRUE) %>%
    inner_join(get_sentiments("nrc")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(y= reorder(sentiment, n), x = n))+geom_col()+
    labs(y='Relative Frequency', x ='')
```
```{r}
d %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(word, sort = TRUE) %>%
    inner_join(get_sentiments("afinn")) %>%
    filter(!is.na(value)) %>%
    count(value, wt = n, sort = TRUE) %>% 
    ggplot(aes(x= value, y = n))+geom_col()+
    labs(y='Frequency', x ='')
```

